---
title: "ImmPort_experimentSamples"
format: html
---

Working this process out programmatically from code to simplify the template completion. 

# treatments.txt

Please note, when no treatment is selected, nothing needs to be inputed in the amounts listed category (took three attempts of the validate tool to figure this one out)

```{r}
Alpha <- "Something"

treatments <- data.frame(
    `User Defined ID`=Alpha, #ICS_PMA
    `Name`=Alpha, #PMA ionomycin with Brefelden Monensin
    `Use Treatment`=Alpha, #Yes
    `Amount Value`=Alpha, # 2
    `Amount Unit`=Alpha, # ul
    `Duration Value`=Alpha, # 6
    `Duration Unit`=Alpha, # Hours
    `Temperature Value`=Alpha, # 37
    `Temperature Unit`=Alpha, # C
    `Comments`=Alpha, #eBioscience Cell Stimulation Cockatail (500x), 2 ul per ml
    check.names=FALSE
)

#Uploading treatments.txt, Cord blood mononuclear cells were treated with golgi transport inhibitors, in the presence or absence of PMA/ionomycin
```

# reagents.Flow_Cytometry.txt

Ok, let's make this easy, and just tidy-rearrange the data from the CordBloodILT repo:

```{r}
library(dplyr)
Panel <- read.csv("ImmPort/ILT_Antibody_Panels.csv", check.names=FALSE)
Panel <- Panel |> mutate(UserDefinedID=paste(Fluorophore, Marker, sep=" ")) |> relocate(UserDefinedID, .before=1) |> filter(Panel %in% "Spectral")
colnames(Panel)

Panel1 <- Panel |> select(UserDefinedID, Manufacturer, Catalog.Number, Marker, Clone, Fluorophore)
Panel2 <- Panel1 |> mutate(Name="", Description="", LotNumber="", Weblink="", Contact="", AntibodyRegistryID="") |> relocate(Name, Description, .after=UserDefinedID) |> relocate(LotNumber, Weblink, Contact, .after=Catalog.Number) |> relocate(AntibodyRegistryID, .after=Marker)
write.csv(Panel2, "ImmPort/CompletedTemplates/IntermediateReagents.csv", row.names=FALSE)

# Reagents for the spectral flow cytometry panel
```

From there, copy paste over, and edit the markers that are present on the list. 

# subjectHumans.txt

```{r}
UserDefinedID = "study_1716"
HEU-hi = "arm-cohort_1716_1" # ARM11928
HEU-lo = "arm-cohort_1716_2" # ARM11929
HU = "arm-cohort_1716_3" # ARM11930

Birth = "plannedvisit_1716_1"
```

```{r}
Alpha <- "Something"

subjectHumans <- data.frame(
    `Subject ID` = Alpha, #INF191, ND006, etc.
    `ArmOrCohortID`=Alpha, #HEU status
    `Sex`=Alpha, #Female, Male
    `Min Subject Age`=Alpha, #0
    `Max Subject Age`=Alpha,
    `Age Unit`=Alpha, #Days ?
    `Age Event`=Alpha, #Age at Study Day 0
    `Age Event Specificity`=Alpha,
    `Subject Phenotype`=Alpha,
    `Subject Location`=Alpha, # Malawi #US: Maryland
    `Ethnicity`=Alpha, #Not Hispanic or Latino
    `Race`=Alpha, #Black or African American
    `Race Specificity`=Alpha,
    `Description`=Alpha,
    `Result Separator Column`=NULL,
    `Exposure Process Reported`=Alpha,
    `Exposure Material Reported`=Alpha,
    `Disease Reported`=Alpha,
    `Disease Ontology ID`=Alpha,
    `Disease Stage Reported`=Alpha,
    check.names = FALSE
)
```


```{r}
External <- file.path("E:", "ImmPort")
Experiments <- list.files(path=External, include.dirs=TRUE, full.names=TRUE)
x <- Experiments[1]
```

```{r}
ProcessingFunction <- function(x){
    ListFiles <- list.files(x)
}
```

Sigh... why is my solution to everything.... turn it into an R package *laugh*

```{r}
Alpha <- "Example Text"

experimentSamples.Flow_Cytometry <- data.frame(
    `ExpSample ID` = Alpha,
    `Biosample ID` = Alpha,
    `Experiment ID` = Alpha,
    `Reagent IDs` = Alpha,
    `Treatment IDs` = Alpha,
    `FCS Result File` = Alpha,
    `Compensation or Control File Names` = Alpha,
    `Expsample Name`= Alpha,
    `Expsample Description`= Alpha,
    `Additional Result File Names`= Alpha,
    `Study ID` = Alpha,
    `Protocol ID` = Alpha,
    `Subject ID` = Alpha,
    `Planned Visit ID` = Alpha,
    `Type`= c("Cord blood", "PBMC"),
    `Subtype`= Alpha,
    `Biosample Name` = Alpha,
    `Biosample Description`= Alpha,
    `Study Time Collected`= Alpha,
    `Study Time Collected Unit`= Alpha,
    `Study Time to Event` = Alpha,
    `Study Time to Event Specificity` = Alpha,
    `Experiment Name` = Alpha,
    `Experiment Description`= Alpha,
    `Measurement Technique` = "Spectral Flow Cytometry",
     check.names=FALSE)
```

